\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
wording in filtering

The raw signal is the calcium fluorescence imaging representing neuron
activity via a capture imaging process. Observing the fluorescent calcium as
an indicator of neuron activity delivers a 2-D view of neuron network at each
capture which only gives a network screenshot at given time points. It implies
obvious issues. Some neurons may be invisible because they are not observed or
they are confounded with another one because of the loss of the third
dimension. The capture sample rate is also a constraint that could make
difficult to detect in which order the neurons fire.  Moreover the activity
indicator is highly reactive to a burst but takes some time to recover its non
active state.  Finally, the difficulty to distinguish direct relationships when there is a network burst, defined as a highly synchronous activity [Stetter and in Stetter [20,46,47]], is increased by the slow sampling rate.

>>>>

The raw signal is the calcium fluorescence imaging representing neuron
activity via a capture imaging process. Observing the fluorescent calcium as
an indicator of neuron activity delivers a 2-D view of neuron network at each
capture which only gives a network screenshot at given time points. It implies
obvious issues. Some neurons may be invisible because they are not observed or
they are confounded with another one because of the loss of the third
dimension. The capture sample rate is also a constraint that could make
difficult to detect in which order the neurons fire.  Moreover the activity
indicator is highly reactive to a burst but takes some time to recover its non
active state.  Finally, the difficulty to distinguish direct relationships when a network burst happens, defined as a highly synchronous activity [Stetter and in Stetter [20,46,47]], is increased by the slow sampling rate.
